---
title: 'UNHCR PA: Data Collection Tracker'
author: "REACH"
date: "2022-11-08"
output:  
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(dirname(inputFile), '/pa_field_data_collection_tracker_', format(Sys.Date(), '%Y_%m_%d'),'.html')) })
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = F, message = F)

# read packages
library(tidyverse)
library(lubridate)
library(glue)
library(leaflet)

# read data 

df_settlement_samples <- readr::read_csv("../inputs/Refugee_PA_survey_samples_definition.csv") %>% 
  filter(!is.na(settlement), sample_size > 0)

df_for_colnames <- df_settlement_samples %>% 
  mutate(district_name = str_to_lower(District),
         district_name = str_replace_all(string = district_name, pattern = " ", replacement = "_"),
         refugee_settlement = str_to_lower(settlement),
         refugee_settlement = str_replace_all(string = refugee_settlement, pattern = " ", replacement = "_")) %>% 
  select(district_name, refugee_settlement) %>% 
  unique()

df_settlement_samples_required <- df_settlement_samples %>% 
  rename(refugee_settlement = settlement) %>% 
  select(refugee_settlement, sample_size) %>% 
  mutate(refugee_settlement = str_to_lower(refugee_settlement),
         refugee_settlement = str_replace_all(string = refugee_settlement, pattern = " ", replacement = "_")
         )



df_tool_data <- readxl::read_excel("../inputs/UNHCR_PA_Assessment_Data.xlsx") %>% 
  mutate(uuid = `_uuid`,
         start_date = as_date(start),
         start = as_datetime(start),
         end = as_datetime(end),
         latitude = as.numeric(`_geopoint_latitude`),
         longitude = as.numeric(`_geopoint_longitude`)) %>% 
  filter(consent_two == "yes",
         start_date > as_date("2022-07-27"), 
         !str_detect(string = point_number, pattern = fixed('test', ignore_case = TRUE))
         )    

# days that contain data
df_days_for_data_collection <- df_tool_data %>% select(start_date) %>% unique() %>% arrange(start_date) %>% pull()

df_data_support_cl_log <- df_tool_data %>% 
  select(uuid, refugee_settlement, latitude,	longitude )
# cleaning log handling
df_cl_log <- read_csv(file = "../inputs/combined_checks_pa.csv") %>% 
  mutate(adjust_log = ifelse(is.na(adjust_log), "apply_suggested_change", adjust_log)) %>% 
  left_join(df_data_support_cl_log, by = "uuid")

# change_response logs that affect stats in the data collection progress
cl_log_change_response <- df_cl_log %>% 
  filter(type == "change_response", 
         !is.na(value),
         reviewed == 1, 
         adjust_log != "delete_log", 
        ) %>% 
  select(uuid, name, value)

# updated tool data
df_updated_tool_data <- df_tool_data

# get uuids from cleaning log
uuids_chg_response <- cl_log_change_response %>% pull(uuid) %>% unique()

for (current_uuid in uuids_chg_response) {
  current_uuid_data <- cl_log_change_response %>% 
    filter(uuid == current_uuid) %>% 
    mutate(value = ifelse(name == "enumerator_id", as.numeric(value), value)) %>% 
    pivot_wider(names_from = "name", values_from = "value", uuid)
  print(current_uuid_data)
  # process current updates
  df_current_updated <- df_updated_tool_data %>% 
    rows_update(y = current_uuid_data, by = "uuid")
  # update the parent dataset with current updates
  df_updated_tool_data <- df_current_updated
}

# enumerator performance data
df_enum_performance <- df_updated_tool_data %>% 
  mutate(int.survey_time_interval = lubridate::time_length(end - start, unit = "min"),
         int.survey_time_interval = ceiling(int.survey_time_interval))

# functions for changing some options in the table
dt_set_options<- function(x){
  DT::datatable(x,
                options = list(
                  autoWidth=F,
                  dom= 't',
                  list(list(width = '20%', targets = list(1,2,3,4,5)))
                )
  )
}

dt_with_modified_options <- function(x){
  DT::datatable(x,
                rownames = FALSE,
                options = list(
                  # columnDefs = list(list(className = 'dt-center', targets = list(1,2,3,4,5))),
                  pageLength = 20,
                  initComplete = JS(
                    "function(settings, json) {",
                    "$(this.api().table().header()).css({'background-color': '#333', 'color': '#fff'});",
                    "}")
                )
  )
}

dt_options_fewcols <- function(x){
  DT::datatable(x,
                rownames = FALSE,
                options = list(
                  pageLength = 20,
                  initComplete = JS(
                    "function(settings, json) {",
                    "$(this.api().table().header()).css({'background-color': '#333', 'color': '#fff'});",
                    "}")
                )
  )
}

dt_enum_performance_options <- function(x){
  DT::datatable(x,
                rownames = FALSE,
                filter = 'top',
                options = list(
                  columnDefs = list(list(className = 'dt-center', targets = list(1,2))),
                  pageLength = 50,
                  initComplete = JS(
                    "function(settings, json) {",
                    "$(this.api().table().header()).css({'background-color': '#333', 'color': '#fff'});",
                    "}"),
                  order = list(list(1, 'desc'), list(0, 'asc'), list(3, 'desc'))
                )
  )
}
```


## Summary on the surveys done

>There are **`r nrow(df_updated_tool_data)`** total number of surveys done as of **`r df_days_for_data_collection[length(df_days_for_data_collection)]`**.

### Settlements:  **`r df_updated_tool_data %>% nrow()`** surveys

```{r, echo = FALSE}

df_refugee_samp_per_settlement <- df_settlement_samples_required %>% 
  group_by(refugee_settlement) %>% 
  summarise(required_samples = sum(sample_size, na.rm = TRUE))


df_cl_surveys_for_deletion <- df_cl_log %>%
  filter(type == "remove_survey", reviewed == 1, !adjust_log %in% c("delete_log")) %>%
  group_by(refugee_settlement) %>%
  distinct(uuid) %>%
  summarise(surveys_for_deletion = n())


df_updated_tool_data %>%
  group_by(district_name, refugee_settlement) %>%
  summarise(number_of_surveys = n()) %>%
  arrange(district_name) %>%
  right_join(df_refugee_samp_per_settlement, by = "refugee_settlement") %>%
  left_join(df_cl_surveys_for_deletion, by = "refugee_settlement") %>%
  mutate(number_of_surveys = ifelse(is.na(number_of_surveys), 0, number_of_surveys),
         surveys_for_deletion = ifelse(is.na(surveys_for_deletion), 0, surveys_for_deletion),
         int.surveys_and_deletion = number_of_surveys - surveys_for_deletion,
         remaining_surveys = required_samples - int.surveys_and_deletion ) %>%
  left_join(df_for_colnames, by = "refugee_settlement") %>% 
  # select(-refugee_settlement) %>%
  rename(district_name = district_name.x) %>%
  mutate(district_name = district_name.y) %>%
  select(-c(int.surveys_and_deletion, district_name.y)) %>%
  dt_with_modified_options()
```


### Daily enumerator performance

The average survey time for all the data is: **`r round(mean(df_enum_performance$int.survey_time_interval), 0)`** Minutes

```{r, echo = FALSE}

df_enum_performance %>% 
  group_by(district_name, start_date, enumerator_id) %>% 
  summarise(number_of_interviews_done = n(), `average_survey_time(minutes)` = round(mean(int.survey_time_interval, na.rm = TRUE), 0)) %>% 
  dt_enum_performance_options()
```

## Looking into the cleaning log

### Number of issues by issue_id

```{r, echo = FALSE}
df_cl_log %>% 
  group_by(issue_id) %>% 
  summarise(number_of_issues_by_issue_id = n()) %>%
  arrange(desc(number_of_issues_by_issue_id)) %>% 
  dt_options_fewcols()
```
### Number of issues by enumerator

```{r, echo = FALSE}
df_cl_log %>% 
  group_by(enumerator_id) %>% 
  summarise(number_of_issues_by_enumerator_id = n()) %>%
  arrange(desc(number_of_issues_by_enumerator_id)) %>% 
  dt_options_fewcols()
```

### Number of issues by enumerator and issue_id

```{r, echo = FALSE}
df_cl_log %>% 
  group_by(enumerator_id, issue_id) %>% 
  summarise(number_of_issues_by_enumerator_and_issue_id = n()) %>%
  arrange(desc(number_of_issues_by_enumerator_and_issue_id)) %>% 
  dt_options_fewcols()
```

### Enumerators with surveys for deletion

```{r, echo = FALSE}
df_cl_log %>% 
  filter(type == "remove_survey", reviewed == 1, adjust_log != "delete_log") %>% 
  group_by(enumerator_id) %>% 
  summarise(number_of_surveys_for_deletion_by_enumerator = n()) %>%
  arrange(desc(number_of_surveys_for_deletion_by_enumerator)) %>% 
  dt_options_fewcols()
```

### Map of surveys for deletion

```{r, echo = FALSE, out.width="100%"}
# popup
labels_pts <- ~sprintf(
  "<strong>Settlement Name: %s</strong><br/>
      Point Number :  <strong>%s</strong><br/>
      Issue ID :  <strong>%s</strong><br/>
      Issue :  <strong>%s</strong><br/>
      Enumerator ID :  <strong>%s</strong>",
  refugee_settlement, point_number, issue_id, issue, enumerator_id
) %>%
  lapply(htmltools::HTML)

df_cl_log %>%
  filter(type == "remove_survey", reviewed == 1, adjust_log != "delete_log") %>%
  group_by(uuid, refugee_settlement, latitude, longitude) %>%
  summarise(start_date = paste(start_date, collapse = " : "),
            enumerator_id = paste(enumerator_id, collapse = " : "),
            district_name = paste(district_name, collapse = " : "),
            point_number = paste(point_number, collapse = " : "),
            type = paste(type, collapse = " : "),
            name = paste(name, collapse = " : "),
            current_value = paste(current_value, collapse = " : "),
            value = paste(value, collapse = " : "),
            issue_id = paste(issue_id, collapse = " : "),
            issue = paste(issue, collapse = " : ")
  ) %>%
  unique() %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(~longitude,
                   ~latitude,
                   popup = labels_pts,
                   radius = 10,
                   color = "red",
                   stroke = FALSE, fillOpacity = 0.9,
                   label = labels_pts,
                   clusterOptions = markerClusterOptions())
```



